Project Light

### 2015-09-09 paper/paper.tex
minor fixes in related work section

The \textit{IPv6 over Low-Power Wireless Personal Area Networks (6LoWPAN)} protocol stack as described in \cite{palattella2013standardized} is tailoring this needs.
The criteria for IoT network stacks are according to them: low power usage, high reliability, Internet-suitability.
Therefore, tailored implementations of stack layers are presented, like \textit{PHY of IEEE 802.15.4}, which is a power saving physical/link layer.
In order to be Internet-enabled regarding the need for huge amounts of addresses, IPv6 is utilized.
However, in order to save energy, the headers of IPv6 packets are heavily compressed in 6LoWPAN.

There are some proposals for specialized security measures in this stack, e.g. \textit{Adaptive Key Establish- ment Scheme (AKES)}, \cite{krentz15akes}.
AKES makes use of session keys and a neighborhood-exploration-technique to gain sufficient security level while being memory-space-saving.
Security is even obtained after reboots.
It still relies on predistribution keys on each mote.

@@

\begin{itemize}
	\item \cite{chen2011over} proposes key provisioning using eliptic curve cryptography (ECC). However, while meeting high security standards, software implementations of ECC require a lot of memory space and energy while hardware implementations increase the per-unit cost.
	\item In order to secure radio communication, \cite{kuo2007message} utilizes a Faraday cage in which a mote can be programmed without interleaving of messages from an attacker outside of the cage. Additionally, a third device outside of the cave jams radio waves to prevent malicious communication.
	\item \textit{6doku} is a protocol for pairing  a mote with a touch-enabled devices like an smart phone, \cite{krentz20156doku}. The smart phone needs extra hardware attached for communicating with the mote via radio waves. It relies on interaction with the end-user, e.g. he needs to check if blinking on the screen happens in sync with him pressing a button on the mote.
\end{itemize}

@@

\cite{saxena2009blink} proposes to generate public keys on the mote(s) and transfer them to a \textit{sink} via standard radio channels.
They are then verified using the unidirectional light channel from the motes to the sink.

>>>>

The \textit{IPv6 over Low-Power Wireless Personal Area Networks (6LoWPAN)} protocol stack as described in \cite{palattella2013standardized} is tailoring this needs.
The criteria for IoT network stacks are, according to them: low power usage, high reliability, Internet-suitability.
Therefore, tailored implementations of stack layers are presented, like \textit{PHY of IEEE 802.15.4}, which is a power saving physical/link layer.
In order to be Internet-enabled regarding the need for huge amounts of addresses, IPv6 is utilized.
However, in order to save energy, the headers of IPv6 packets are heavily compressed in 6LoWPAN.

There are some proposals for specialized security measures in this stack, e.g. \textit{Adaptive Key Establishment Scheme (AKES)}, \cite{krentz15akes}.
AKES makes use of session keys and a neighborhood-exploration-technique to gain sufficient security level while being memory saving.
Security is even obtained after reboots of motes, but it relies on predistribution keys on each mote.

@@

\begin{itemize}
	\item \cite{chen2011over} proposes key provisioning using eliptic curve cryptography (ECC). However, while meeting high security standards, software implementations of ECC require a lot of memory space and energy while hardware implementations increase the per-unit cost.
	\item In order to secure radio communication, \cite{kuo2007message} utilizes a Faraday cage in which a batch of motes can be programmed without interleaving of messages from an attacker outside of the cage. Additionally, another device outside of the cave jams radio waves to prevent malicious communication.
	\item \textit{6doku} is a protocol for pairing  a mote with a touch-enabled devices like an smart phone, \cite{krentz20156doku}. The smart phone needs extra hardware attached for communicating with the mote via radio waves. It relies on interaction with the end-user, e.g. he needs to check if blinking on the screen happens in sync with him pressing a button on the mote.
\end{itemize}

@@

\cite{saxena2009blink} proposes to generate public keys on the mote(s) and transfer them to a \textit{sink} via standard radio channels.
They are verified afterwards using the unidirectional light channel from the motes to the sink.
However, they still rely on energy consuming asymmetric encryption.
